Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-14 doc/JFLA2022/paper.tex
starting monorepo pass, fix bridge subsection title

\subsection{Bridge to ordinals in \gaia}

@@

We solved this maintenance issue by moving to \alectr, a tool that automatically records \coq proofs.  Instead of copy-pasting fragments into LaTeX, we now embed small LaTeX files automatically generated by \alectr from our \coq development.  Our build system guarantees that these LaTeX snippets are always up-to-date and consistent with the code (and, by comparing these snippets across releases of \coq or versions of \Hydras, we can easily spot unexpected changes).

@@

Monorepos (shorthand for monolithic repositories) are single repositories containing multiple independent or related packages.
%
They have gained increasing popularity following experiences in large companies such as Google, but are also used at a lesser scale for managing open source projects.
%
They are known to simplify the management of dependencies, making cross-packages changes and refactorings~\cite{brito2018monorepos}.

In the context of Coq projects, they did not use to be well-supported.
%
One of the few early monorepos in the Coq ecosystem was the Mathematical Components (math-comp) repository, which used a custom build infrastructure to check multiple packages on each commit.
%
However, recent improvements in tooling have made their use easier, and therefore we have used them more and more, for instance within \community.

>>>>

\subsection{First steps towards a bridge to \gaia}

@@

We solved this maintenance issue by moving to \alectr, a tool that automatically records \coq proofs~\cite{alectryongithub}.  Instead of copy-pasting fragments into LaTeX, we now embed small LaTeX files automatically generated by \alectr from our \coq development.  Our build system guarantees that these LaTeX snippets are always up-to-date and consistent with the code (and, by comparing these snippets across releases of \coq or versions of \Hydras, we can easily spot unexpected changes).

@@

A monorepo (shorthand for monolithic repository) is a version control repository containing multiple independent or related packages.
%
Monorepos have gained increasing popularity following experiences in large companies such as Google, but are also used at a smaller scale for managing open source projects.
%
They are known to simplify the management of dependencies, making cross-packages changes, and refactorings~\cite{brito2018monorepos}.

%
One of the few early monorepos in the Coq ecosystem was the Mathematical Components (math-comp) repository, which used a custom build infrastructure to check multiple packages on each commit.
%
However, recent improvements in tooling have made their use easier, and therefore we have used them more and more, for instance within \community.
